Constraint Grammar as a SAT problem

### 2015-03-30 paper/nodalida2015.tex
polish intro

We represent Constraint Grammar \cite{karlsson1995constraint} 
as a Boolean satisfiability (SAT) problem.

Formal logic is well-studied and has an old tradition.
The rules encoded in logic capture richer dependencies between the
tags than normal reductionist grammars.

>>>>

We represent Constraint Grammar \cite{karlsson1995constraint} 
as a Boolean satisfiability (SAT) problem.
This is attractive from several reasons: formal logic is
well-studied, and serves as an abstract language to reason about the
properties of CG. Constraint rules encoded in logic capture richer
dependencies between the tags than standard CG.
